Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article.tex
Fix LaTeX

\textbf{GEERT: zie voorgaande punt aangaande verwachtingwaarde. De gevonden waardes zijn hoger, dus zoek je in volgende stuk tekst naar problemen die er niet zijn, en zou dit dus weg laten. Is onduidelijk en wollig stuk: The percentage of TMH derived epitopes is relatively high
for both sources of epitopes, which are (1) the predicted 
9-mers (for MHC-I) and 14-mers (for MHC-II) from
a reference human proteome  (see Figure \ref{fig:bbbq_1_smart_results}),
(2) the IEBD epitopes from MHC ligand assays (Figure \ref{fig:2a}).
These results cannot be compared with an \emp{a priori}
expactation, as the predicted percentages are biased by
(I) the expression of the probed proteins and cleavage sites, 
(II) the bias in mass spectrometry towards hydrophillic peptides 
and (III) availablilty of data for the different alleles.}

>>>>

\textbf{GEERT: zie voorgaande punt aangaande verwachtingwaarde. De gevonden waardes zijn hoger, dus zoek je in volgende stuk tekst naar problemen die er niet zijn, en zou dit dus weg laten. Is onduidelijk en wollig stuk: The percentage of TMH derived epitopes is relatively high
for both sources of epitopes, which are (1) the predicted 
9-mers (for MHC-I) and 14-mers (for MHC-II) from
a reference human proteome  (see Figure \ref{fig:bbbq_1_smart_results}),
(2) the IEBD epitopes from MHC ligand assays (Figure \ref{fig:2a}).
These results cannot be compared with an \emph{a priori}
expactation, as the predicted percentages are biased by
(I) the expression of the probed proteins and cleavage sites, 
(II) the bias in mass spectrometry towards hydrophillic peptides 
and (III) availablilty of data for the different alleles.
}
